Breast Cancer Diagnosis Classification Analysis

### 2022-12-09 powerpoint.rmd
update 2

---
```{r setup, include=FALSE}
# Import packages
library(tidyverse)
library(ggplot2)
library(GGally)
library(knitr)
library(boot)
library(caret)
library(randomForest)
library(e1071)
library(class)
set.seed(420)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 14, fig.height = 8)
```

@@

- Many people are diagnosed with breast cancer each year
- Breast Cancer Diagnosis Data
- Predict Diagnosis of Tumor based on features (Malignant or Benign)
- *Modivation:* Reduce Type II Error (False-Negatives)
  - Feature and Model Selection

@@

```{r}
ggplot(train) +
  geom_point(aes(x = concavity_mean, y = radius_mean, col = diagnosis))+
  labs(x = "Concavity Mean", y = "Radius Mean", title = "Severity of Concavity vs. Radius of Tumor")
```

@@

@@

@@

```{r}
### Random Forest

rf_spec <- rand_forest(mtry = sqrt(.cols())) |>
  set_engine("randomForest", importance = TRUE) |>
  set_mode("classification")

@@

```{r, echo = F}
ggplot(data.frame(rf.cm$table), aes(x = Prediction, y = Truth, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = Freq), size = 12) +
  scale_fill_gradient(low = "white", high = "#c82798") +
  labs(title = "Random Forest Confusion Matrix", x = "Prediction", y = "Truth") +
  theme_minimal() +
  theme(axis.text = element_text(size = 20), axis.title = element_text(size = 30), plot.title = element_text(size = 30)) +
  annotate("path",
   x=1+.25*cos(seq(0,2*pi,length.out=100)),
   y=2+.25*sin(seq(0,2*pi,length.out=100)), size=1.5, linetype="dashed", color="#c82798") +  
  guides(fill = F)

vip(rf_fit)
```

>>>>

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 14, fig.height = 8)
```

@@

- Breast Cancer Diagnosis Data
- Predict Diagnosis of Tumor based on features
- Reduce Type II Error (False-Negatives)
- Feature Selection

@@

```{r}
ggplot(train) +
  geom_point(aes(x = concavity_mean, y = radius_mean, col = diagnosis))+
  labs(x = "Concavity Mean", y = "Radius Mean", title = "Severity of Concavity vs. Radius of Tumor")

train[,c(1,2,12,22)] |>
  ggpairs()
```

@@

## KNN Confusion Matrix

@@

## SVC Confusion Matrix

@@

```{r}
### Random Forest
set.seed(445)
rf_spec <- rand_forest(mtry = sqrt(.cols())) |>
  set_engine("randomForest", importance = TRUE) |>
  set_mode("classification")

@@

## RF Confusion Matrix

```{r, echo = F}
ggplot(data.frame(rf.cm$table), aes(x = Prediction, y = Truth, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = Freq), size = 12) +
  scale_fill_gradient(low = "white", high = "#c82798") +
  labs(title = "Random Forest Confusion Matrix", x = "Prediction", y = "Truth") +
  theme_minimal() +
  theme(axis.text = element_text(size = 20), axis.title = element_text(size = 30), plot.title = element_text(size = 30)) +
  annotate("path",
   x=1+.25*cos(seq(0,2*pi,length.out=100)),
   y=2+.25*sin(seq(0,2*pi,length.out=100)), size=1.5, linetype="dashed", color="#c82798") +  
  guides(fill = F)
```

## RF Confusion Matrix

```{r, echo = FALSE}
vip(rf_fit)
```
